Maximising the guaranteed feasible set for uncertain MPC schemes with chance constraints

### 2017-02-28 draft.tex
Post-acceptance changes.
what happened

[ticket: X]

\title{Maximising the guaranteed feasible set for stochastic MPC with chance constraints}%\thanksref{footnoteinfo}} 
% Title, preferably not more than 10 words.

@@

\begin{keyword}                           % Five to ten keywords,  
Robust control; chance constraints;  invariant sets; stochastic MPC.
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

\section{Introduction}
%
%
Positively invariant sets for uncertain linear systems have been researched for several decades, see e.g.~\cite{Kolmanovsky:1995,Kolmanovsky:1998,blanchini:2007}.
%
The properties of such sets and the algorithms to compute them are well known and are documented in the literature.
%
As well as being objects of interest in their own right,
%In addition to pure analysis purposes, 
these sets are often used as terminal constraint sets in Model Predictive Control (MPC) in order to guarantee the feasibility of the control scheme at all times \citep[see e.g.][]{Mayne2014}.
%

@@

In order to formulate a robust MPC law for a chance constrained stochastic system while introducing a minimal amount of conservatism, we consider a closed-loop min-max formulation~\citep{Lee:1997}. This requires the determination of additional constraints.
%
The $n$-step controllable set for a given horizon $n$ and target set \citep[see e.g.][]{bertsekas71} has the property that, for every state in the $n$-step controllable set, there exists an admissible input sequence such that the system state enters the target set after $n$ steps, for any admissible sequence of uncertainty realisations.
%
Using a parametrised uncertainty set with specified probabilistic properties, chance constraints can be replaced by computationally convenient set operations that guarantee the satisfaction of the original chance constraints.
%
By maximising the size of the $n$-step controllable set we indirectly approximate the $n$-step controllable set of the chance constrained system.

%The remainder of this paper elaborates the method in the following way:
%
The paper is organised  as follows:
In section~\ref{sec:setup} we present the problem formulation and derive, in section~\ref{ssec:approximating:MRPI}, conditions that define the positively invariant set under chance constraints. The corresponding conditions for the $n$-step controllable set are derived in section~\ref{ssec:approximating:n:step} and these are used to define an MPC law in section~\ref{ssec:mpc}.
%
A parametrisation employing parallelotopes is discussed in section~\ref{sec:volume:of:hypercube} and the general problem formulations introduced in section~\ref{sec:setup} are made precise for this parametrisation.
%
A numerical example is presented in section~\ref{sec:examples} to illustrate the proposed scheme in two dimensions and in section~\ref{sec:conclusion} we conclude the paper and sketch possible extensions to the proposed scheme.

@@

\section{Approximating the guaranteed invariant set}\label{ssec:approximating:MRPI}
%
First we discuss how to extend existing methods to calculate the maximal robust positively invariant (MRPI) set (see e.g.~\cite{blanchini:2007}) in such a way that all states in the MRPI set produce only feasible successor states for a given feedback controller $u = Kx$.
%
Thus we seek to determine a set of initial conditions for which all possible trajectories of (\ref{eq:system}) subject to (\ref{eq:disturbance}) satisfy the robust constraints~(\ref{eq:state_input:constraints}) and probabilistic constraint (\ref{eq:probabilistic:constraint}). Denoting the largest such set as $\Xinfty$ we have
\begin{multline*}
\Xinfty = \Bigl\{x_0\in\X: \\
\begin{aligned}
% &x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i} w_{k-i}\\
% &x_{k+1} = (A+BK)^{k+1} x + \sum_{i=1}^{k+1} (A+BK)^{k+1-i} w_{k+1-i}\\
&x_{k+1} = (A+BK)^{k+1} x_0 + \sum_{i=0}^{k} (A+BK)^{k-i} w_{i}\\
&x_{k+1}\in\X\\
&Kx_k\in\U\\
&\PP\{v\in\V : (C+DK)x_k+v\in\Y\}\geq p 
\end{aligned}\\
\forall w_k\in\W,\, \forall k\geq 0 \Bigr\} .
\end{multline*}
%
% \begin{multline}\label{eq:alternative:MRPI:set}
% 	X^\infty = \Bigl\{x\in\X: \\
% \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_k\in\X\\
% 	&(C+DK)x_k+v\in\Y\\
% 	&\forall w_j\in\W,\ \forall v\in \V^\prime,\ \forall k\geq 0 \Bigr\}
% \end{aligned} 
% \end{multline}
%
% It is obvious that $X^\infty$ contained in the invariant set of the original problem~$\Xinfty$:
For a given set $\V^\prime$, let $X^\infty$ denote the set
%
\begin{multline}\label{eq:alternative:MRPI:set}
	X^\infty = \Bigl\{x_0\in\X: \\
\begin{aligned} 
%&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i} w_{k-i} \\
&x_{k+1} = (A+BK)^{k+1} x_0 + \sum_{i=0}^{k} (A+BK)^{k-i} w_{i} \\
&x_{k+1}\in\X \\ 
&Kx_k\in\U \\
&(C+DK)x_k+v_k\in\Y
\end{aligned}\\
\forall w_k\in\W,\ \forall v_k\in \V^\prime,\ \forall k\geq 0 \Bigr\} .
\end{multline}
% \begin{equation}
% 	\Xinfty = \left\{x\in\X: \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_k\in\X\\
% 	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
% 	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}
% \end{equation}
%
Then from Proposition~\ref{prop1}, the inclusion $X^\infty\subseteq\Xinfty$ necessarily holds for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$. Furthermore, by maximising the volume of $X^\infty$ we can improve the approximation of $\Xinfty$.

In order to determine an algorithm to compute $X^\infty$ we rewrite the conditions in~\eqref{eq:alternative:MRPI:set} by introducing the set of all possible successor states~$\D_k(X)$ of states in $X$ after $k$ time steps:
%
\begin{align*}
	\D_k(X) &= (A+BK)^{k}X\oplus\W\oplus\dots\oplus(A+BK)^{k-1}\W\\
	&= (A+BK)^k X\oplus \bigoplus_{i=0}^{k-1}(A+BK)^i\W
\end{align*}
%
Defining $\R = (C+DK)^{-1}(\Y\ominus\V^\prime)$ we can abbreviate the conditions defining $X^\infty$ in~\eqref{eq:alternative:MRPI:set} to
%
\begin{equation}\label{eq:containment:condition:alternative:MRPI}
\D_k(X^\infty)\subseteq\X\cap\R
\end{equation}
%
for all $k\geq0$.
%
Using these conditions we can express $X^\infty$ directly as
%
\begin{gather}
X^\infty = %\bigcap_{k\geq0}(A+BK)^{-k}\Bigl((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\Bigr) \\
\bigcap_{k\geq0} \E_k, \\
\E_k = (A+BK)^{-k}\biggl[(\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\biggr] . \label{eq:Ek:subtract}
\end{gather}
% \begin{equation}\label{eq:direct:formulation:MRPI:with:intersection}
% 	X^\infty = \bigcap_{k\geq0}\underbrace{(A+BK)^{-k}\left((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\right)}_{\E_k}.
% \end{equation}
%
Due to its definition~$\E_k$ satisfies $\D_k(\E_k)\subseteq\X\cap\R$ for each $k\geq0$, furthermore it can be shown that $\E_k$ expands exponentially and therefore $X^\infty$ is finitely determined  (see Theorem~\ref{thm2} below).
%
In order to compute $X^\infty$ we define the sequence $X_0,X_1,\ldots$ via the iteration:
%
\begin{equation}\label{eq:MRPI:sequence}
\begin{aligned}
  & X_0 = \X\cap K^{-1}\mathcal U \\
  & \begin{aligned}
      & Z_k = X_k\cap\R\\
      & X_{k+1} = Z_k\cap(A+BK)^{-1}(Z_k\ominus\W)
    \end{aligned} 
  \ \Biggr\} \ \ k = 1,2,\ldots
\end{aligned}
\end{equation}
%
%with $X_0= \X$.
Clearly $X_k = \bigcap_{l=0,\ldots,k}\E_l$ and, analogously to the conventional MRPI calculation~\citep{Kolmanovsky:1998}, the iteration therefore gives $X_k = X^\infty$ if $X_k\subseteq X_{k+1}$.

@@

\section{Approximating the guaranteed $n$-step controllable set}\label{ssec:approximating:n:step}
%
We now turn our attention to the $n$-step controllable set~$\C_n(\T)$ for a given target set~$\T$.
%
%That is the set of initial conditions $x_0\in\C_n(\T)$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, $x_n\in\T$, for all admissible disturbance sequences 
%$w\in\W$, while guaranteeing that the robust state and input constraints~(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
%
This is defined as the set of initial states $x_0$ of (\ref{eq:system}) such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, so that $x_n\in\T$ for all admissible disturbance sequences 
$w_k\in\W$, $k=0,\ldots,n-1$, while guaranteeing that the robust state and input constraints 
%$x_k\in\X$, $u_k\in\U$
(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
%
Thus $\C_n(\T)$ can be expressed as follows.
%
\begin{multline*}
\C_n(\T) = \Bigl\{x_0\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
\begin{aligned}
&x_{k+1} = A^{k+1} x_0 + \sum_{i=0}^{k} A^{k-i}B u_{i}(x_{i}) + \sum_{i=0}^{k} A^{k-i} w_{i}\\
&x_n\in\T\\
&x_{k+1}\in\X\\
&u_k(x_k)\in\U\\
&\PP\bigl\{v\in\V : Cx_k + Du_k(x_k) +v \in\Y\bigr\}\geq p
\end{aligned}\\
\forall w_k\in\W,\, \forall k\in\{ 0, \ldots , n-1\} \Bigr\}	
\end{multline*}
% \begin{equation}
% 	\C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_N\in\T\\
% 	&x_k\in\X\\
% 	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
% 	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}	
% \end{equation}
%
Using Proposition~\ref{prop1} it is easy to verify that the set $C_n(\T)$ defined by
%
\begin{multline*}
C_n(\T) = \Bigl\{ x_0\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
\begin{aligned}
&x_{k+1} = A^{k+1} x_0 + \sum_{i=1}^{k} A^{k-i}B u_{i}(x_{i}) + \sum_{i=1}^{k} A^{k-i} w_{i}\\
&x_N\in\T\\
&x_{k+1}\in\X\\
&u_k(x_k)\in\U \\
&Cx_k+Du_k(x_k) + v_k \in\Y
\end{aligned}\\
\forall w_k\in\W,\, \forall v_k\in \V^\prime,\, \forall k\in\{0,\dots,n-1\} \Bigr\}	
\end{multline*}
% \begin{equation}
% 	C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_N\in\T\\
% 	&x_k\in\X\\
% 	&(C+DK)x_k+v\in\Y\\
% 	&\forall w_j\in\W,v\in \V^\prime,k\in\{0,\dots,N\}\end{aligned} \right\}	
% \end{equation}
%
is necessarily contained in $\C_n(\T)$ for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$.
%
As in the case of positively invariant sets, fixing $\V^\prime$ to be a polytopic set leads to a computationally tractable optimisation for the maximisation of~$C_n$. This suggests an algorithm for constructing $C_n$ as a polytopic approximation of~$\C_n$ by optimising~$\V^\prime$ so as to maximise the volume of~$C_n$.
% indirectly improves the approximation of $\C_n$.
%
It is known that 
%$C_n(\T) = C^n_1(\T) \doteq C_1(C_1(\cdots C_1(\T)\cdots))$ 
$C_n(\T) = C^n_1(\T) \doteq C_1 \circ C_1 \circ \cdots \circ C_1(\T)$ 
\citep[see e.g.][]{blanchini:2007}, which allows the use of simple computational geometry algorithms.

In particular, the one-step controllable set $C_1(\T)$ for a polytopic
target set~$\T$
% \[
% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
% \]
% is given by the projection of 
%
%In particular, the one-step controllable set $C_1(\T)$ for the polytopic target set~$\T$
% \[
% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
% \]
is given by the projection on to the $x$-subspace of the polytopic set $L_1(\T)\subset \RR^{d+q_{\U}}$, 
%$L_1(\T)\subset \RR^d\times \RR^{q_{\U}}$, 
defined by
%
\begin{multline*}
L_1(\T) = \Bigl\{(x,u)\in (\X,\U): \\
\begin{aligned}
& Cx+Du + v\in\Y \\
& Ax+Bu+w\in\T
\end{aligned}\\
\forall v\in\V^\prime,\, \forall w\in\W\Bigr\} .
%\end{aligned}
\end{multline*}
% \begin{equation}
% 	L_1(\T) = \left\{(x,u):\begin{aligned}
% 	x\in\X, u\in\U, Cx+Du + v\in\Y\;\forall v\in\V^\prime,\\
% 	Ax+Bu+w\in\T\;\forall w\in\W
% 	\end{aligned}\right\}
% \end{equation}
%
%onto the $x$-subspace.
%
Thus
\[
C_1(\T) = \{ x\in\mathcal X : \exists u \ \text{such that} \ (x,u)\in L_1(\T)\}.
\]
As all involved sets are polytopic, $L_1(\T)$ is polytopic and its exact projection can be determined computationally.

A set $C_n(\T)$ approximating the $n$-step controllable set $\C_n(\T)$ is then given by the solution of the optimisation:
%
\begin{subequations}\label{seq:optimisation:n:step:set:abstract}
\begin{align}
	& \max_{\V^\prime} \vol(C_n(\T))
%\end{equation}
\intertext{subject to}
%\begin{align}
	& \V^\prime\subseteq\V  \\
% \end{equation}
% %
% \begin{equation}
	& \vol(\V^\prime)\geq p\cdot\vol(\V)
\end{align}
\end{subequations}
The property $C_n(\T)\subseteq \C_n(\T)$ guarantees the existence of a control sequence such that the constraints~(\ref{eq:state_input:constraints}) and (\ref{eq:probabilistic:constraint}) are met and $x_n\in\T$ for all $x_0\in C_n(\T)$.

@@

The underlying probability distribution was assumed to be uniform for ease of presentation, a similar method may be applied to more general distributions as long as they allow the probability measure of a parallelotope to be analytically determined.
%
Future work will remove this restriction by approximating non-uniform probability densities as discrete distributions defined by collections of spatially distributed point masses.
%
This would necessarily introduce a degree of uncertainty in the probability measure of $\V^\prime$. However the uncertainty would be subject to deterministic bounds (rather than the statistical bounds provided by a sample based approach), which would allow for a deterministic guarantee of constraint satisfaction.

>>>>

\title{Maximising the guaranteed feasible set for uncertain MPC schemes with chance constraints}%\thanksref{footnoteinfo}} 
% Title, preferably not more than 10 words.

@@

\begin{keyword}                           % Five to ten keywords,  
Keyword 1; keyword 2;
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

\section{Introduction}
%
%
Positively invariant sets for uncertain linear systems have been researched for several decades, see e.g.~\cite{Kolmanovsky:1995,Kolmanovsky:1998,blanchini:2007}.
%
The properties of such sets and the algorithms to compute them are well known and documented in the literature.
%
As well as being objects of interest in their own right,
%In addition to pure analysis purposes, 
these sets are often used as terminal constraint sets in Model Predictive Control (MPC) in order to guarantee the feasibility of the control scheme at all times \citep[see e.g.][]{Mayne2014}.
%

@@

In order to formulate a robust MPC law for a chance constrained stochastic system while introducing a minimal amount of conservatism, we consider a closed-loop min-max formulation~\citep{Lee:1997}. This requires the determination of additional constraints.
%
The $n$-step controllable set for a given horizon $n$ and target set \citep[see e.g.][]{bertsekas71} has the property that, for every state in the $n$-step controllable set, there exists an admissible input sequence such that the system state enters the target set after $n$ steps, for any admissible sequence of uncertainty realisations.
%
Using a parametrised uncertainty set with specified probabilistic properties, chance constraints can be replaced by computationally convenient set operations that guarantee the satisfaction of the original chance constraints.
%
By maximising the size of the $n$-step controllable set we indirectly approximate the $n$-step controllable set of the probabilistically constrained system.

%The remainder of this paper elaborates the method in the following way:
%
This paper is organised  as follows:
In section~\ref{sec:setup} we present the problem formulation and derive, in section~\ref{ssec:approximating:MRPI}, conditions that define the positively invariant set under chance constraints. The corresponding conditions for the $n$-step controllable set are derived in section~\ref{ssec:approximating:n:step} and these are used to define an MPC law in section~\ref{ssec:mpc}.
%
The parametrisation of a parallelotope is discussed in~\ref{sec:volume:of:hypercube} and the general problem formulations introduced in section~\ref{sec:setup} are made precise for this parametrisation.
%
Two numerical examples are presented in section~\ref{sec:examples} to illustrate the proposed scheme in two dimensions and in section~\ref{sec:conclusion} we conclude the presentation and sketch possible extensions to the presented scheme.

@@

\section{Approximating the guaranteed invariant set}\label{ssec:approximating:MRPI}
%
First we discuss how to extend existing methods to calculate the maximal robust positively invariant (MRPI) set (see e.g.~\cite{blanchini:2007}) in such a way that all states in the MRPI set produce only feasible successor states for a given feedback controller $u = Kx$.
%
Thus we seek to determine a set of initial conditions for which all possible trajectories of (\ref{eq:system}) subject to (\ref{eq:disturbance}) satisfy the robust constraints~(\ref{eq:state_input:constraints}) and probabilistic constraint (\ref{eq:probabilistic:constraint}). Denoting the largest such set as $\Xinfty$ we have
\begin{multline*}
\Xinfty = \Bigl\{x_0\in\X: \\
\begin{aligned}
% &x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i} w_{k-i}\\
% &x_{k+1} = (A+BK)^{k+1} x + \sum_{i=1}^{k+1} (A+BK)^{k+1-i} w_{k+1-i}\\
&x_{k+1} = (A+BK)^{k+1} x_0 + \sum_{i=0}^{k} (A+BK)^{k-i} w_{i}\\
&x_{k+1}\in\X\\
&Kx_k\in\U\\
&\PP\{v\in\V : (C+DK)x_k+v\in\Y\}\geq p 
\end{aligned}\\
\forall w_k\in\W,\, \forall k\geq 0 \Bigr\} .
\end{multline*}
%
% \begin{multline}\label{eq:alternative:MRPI:set}
% 	X^\infty = \Bigl\{x\in\X: \\
% \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_k\in\X\\
% 	&(C+DK)x_k+v\in\Y\\
% 	&\forall w_j\in\W,\ \forall v\in \V^\prime,\ \forall k\geq 0 \Bigr\}
% \end{aligned} 
% \end{multline}
%
% It is obvious that $X^\infty$ contained in the invariant set of the original problem~$\Xinfty$:
For a given set $\V^\prime$, let $X^\infty$ denote the set
%
\begin{multline}\label{eq:alternative:MRPI:set}
	X^\infty = \Bigl\{x_0\in\X: \\
\begin{aligned} 
%&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i} w_{k-i} \\
&x_{k+1} = (A+BK)^{k+1} x_0 + \sum_{i=0}^{k} (A+BK)^{k-i} w_{i} \\
&x_{k+1}\in\X \\ 
&Kx_k\in\U \\
&(C+DK)x_k+v_k\in\Y
\end{aligned}\\
\forall w_k\in\W,\ \forall v_k\in \V^\prime,\ \forall k\geq 0 \Bigr\} .
\end{multline}
% \begin{equation}
% 	\Xinfty = \left\{x\in\X: \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_k\in\X\\
% 	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
% 	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}
% \end{equation}
%
Then from Proposition~\ref{prop1}, the inclusion $X^\infty\subseteq\Xinfty$ necessarily holds for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$. Furthermore, by maximising the volume of $X^\infty$, we can improve the approximation of $\Xinfty$.

In order to determine an algorithm to compute $X^\infty$ we rewrite the conditions in~\eqref{eq:alternative:MRPI:set} by introducing the set of all possible successor states~$\D_k(X)$ of states in $X$ after $k$ time steps:
%
\begin{align*}
	\D_k(X) &= (A+BK)^{k}X\oplus\W\oplus\dots\oplus(A+BK)^{k-1}\W\\
	&= (A+BK)^k X\oplus \bigoplus_{i=0}^{k-1}(A+BK)^i\W
\end{align*}
%
Defining $\R = (C+DK)^{-1}(\Y\ominus\V^\prime)$ we can abbreviate the conditions defining $X^\infty$ in~\eqref{eq:alternative:MRPI:set} to
%
\begin{equation}\label{eq:containment:condition:alternative:MRPI}
\D_k(X^\infty)\subseteq\X\cap\R
\end{equation}
%
for all $k\geq0$.
%
Using these conditions we can express $X^\infty$ directly as
%
\begin{gather}
X^\infty = %\bigcap_{k\geq0}(A+BK)^{-k}\Bigl((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\Bigr) \\
\bigcap_{k\geq0} \E_k, \\
\E_k = (A+BK)^{-k}\biggl[(\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\biggr] . \label{eq:Ek:subtract}
\end{gather}
% \begin{equation}\label{eq:direct:formulation:MRPI:with:intersection}
% 	X^\infty = \bigcap_{k\geq0}\underbrace{(A+BK)^{-k}\left((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\right)}_{\E_k}.
% \end{equation}
%
Due to its definition~$\E_k$ satisfies $\D_k(\E_k)\subseteq\X\cap\R$ for each $k\geq0$, furthermore it can be shown that $\E_k$ expands exponentially and therefore $X^\infty$ is finitely determined  (see Theorem~\ref{thm2} below).
%
In order to compute $X^\infty$ we define the sequence $X_0,X_1,\ldots$ via the iteration:
%
\begin{equation}\label{eq:MRPI:sequence}
\begin{aligned}
  & X_0 = \X\cap K^{-1}\mathcal U \\
  & \begin{aligned}
      & Z_k = X_k\cap\R\\
      & X_{k+1} = Z_k\cap(A+BK)^{-1}(Z_k\ominus\W)
    \end{aligned} 
  \ \Biggr\} \ \ k = 1,2,\ldots
\end{aligned}
\end{equation}
%
%with $X_0= \X$.
Clearly $X_k = \bigcap_{l=0,\ldots,k}\E_l$ and, analogously to the conventional MRPI calculation~\citep{Kolmanovsky:1998}, the iteration therefore gives $X_k = X^\infty$ once $X_k\subseteq X_{k+1}$.

@@

\section{Approximating the guaranteed $n$-step controllable set}\label{ssec:approximating:n:step}
%
We now turn our attention to the $n$-step controllable set~$\C_n(\T)$ for a given target set~$\T$.
%
That is the set of initial conditions $x_0\in\C_n(\T)$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, $x_n\in\T$, for all admissible disturbance sequences 
$w\in\W$, while guaranteeing that the robust state and input constraints~(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
%
This is defined as the set of initial conditions $x_0\in\X$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, so that $x_n\in\T$ for all admissible disturbance sequences 
$w_k\in\W$, $k=0,\ldots,n-1$, while guaranteeing that the robust state and input constraints 
%$x_k\in\X$, $u_k\in\U$
(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
%
Thus $\C_n(\T)$ can be expressed as follows.
%
\begin{multline*}
\C_n(\T) = \Bigl\{x_0\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
\begin{aligned}
&x_{k+1} = A^{k+1} x_0 + \sum_{i=0}^{k} A^{k-i}B u_{i}(x_{i}) + \sum_{i=0}^{k} A^{k-i} w_{i}\\
&x_n\in\T\\
&x_{k+1}\in\X\\
&u_k(x_k)\in\U\\
&\PP\bigl\{v\in\V : Cx_k + Du_k(x_k) +v \in\Y\bigr\}\geq p
\end{aligned}\\
\forall w_k\in\W,\, \forall k\in\{ 0, \ldots , n-1\} \Bigr\}	
\end{multline*}
% \begin{equation}
% 	\C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_N\in\T\\
% 	&x_k\in\X\\
% 	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
% 	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}	
% \end{equation}
%
Using Proposition~\ref{prop1} it is easy to verify that the set $C_n(\T)$ defined by
%
\begin{multline*}
C_n(\T) = \Bigl\{ x_0\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
\begin{aligned}
&x_{k+1} = A^{k+1} x_0 + \sum_{i=1}^{k} A^{k-i}B u_{i}(x_{i}) + \sum_{i=1}^{k} A^{k-i} w_{i}\\
&x_N\in\T\\
&x_{k+1}\in\X\\
&u_k(x_k)\in\U \\
&Cx_k+Du_k(x_k) + v_k \in\Y
\end{aligned}\\
\forall w_k\in\W,\, \forall v_k\in \V^\prime,\, \forall k\in\{0,\dots,n-1\} \Bigr\}	
\end{multline*}
% \begin{equation}
% 	C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_N\in\T\\
% 	&x_k\in\X\\
% 	&(C+DK)x_k+v\in\Y\\
% 	&\forall w_j\in\W,v\in \V^\prime,k\in\{0,\dots,N\}\end{aligned} \right\}	
% \end{equation}
%
is necessarily contained in $\C_n(\T)$ for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$.
%
As in the case of positively invariant sets, fixing $\V^\prime$ to be a polytopic set leads to a computationally tractable optimisation for the maximisation of~$C_n$. This suggests an algorithm for constructing $C_n$ as a polytopic approximation of~$\C_n$ by optimising~$\V^\prime$ so as to maximise the volume of~$C_n$.
% indirectly improves the approximation of $\C_n$.
%
It is known that 
%$C_n(\T) = C^n_1(\T) \doteq C_1(C_1(\cdots C_1(\T)\cdots))$ 
$C_n(\T) = C^n_1(\T) \doteq C_1 \circ C_1 \circ \cdots \circ C_1(\T)$ 
\citep[see e.g.][]{blanchini:2007}, which allows the use of simple computational geometry algorithms.

In particular the one-step controllable set $C_1(\T)$ for a polytopic~$\T$
% \[
% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
% \]
is given by the projection of 
%
In particular, the one-step controllable set $C_1(\T)$ for the polytopic target set~$\T$
% \[
% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
% \]
is given by the projection of
$L_1(\T)\subset \RR^{d+q_{\U}}$, 
%$L_1(\T)\subset \RR^d\times \RR^{q_{\U}}$, 
defined by
%
\begin{multline*}
L_1(\T) = \Bigl\{(x,u)\in (\X,\U): \\
\begin{aligned}
& Cx+Du + v\in\Y \\
& Ax+Bu+w\in\T
\end{aligned}\\
\forall v\in\V^\prime,\, \forall w\in\W\Bigr\} ,
%\end{aligned}
\end{multline*}
% \begin{equation}
% 	L_1(\T) = \left\{(x,u):\begin{aligned}
% 	x\in\X, u\in\U, Cx+Du + v\in\Y\;\forall v\in\V^\prime,\\
% 	Ax+Bu+w\in\T\;\forall w\in\W
% 	\end{aligned}\right\}
% \end{equation}
%
onto the $x$-subspace.
%
Thus
\[
C_1(\T) = \{ x\in\mathcal X : \exists u \ \text{such that} \ (x,u)\in L_1(\T)\}.
\]
As all involved sets are polytopic, $L_1(\T)$ is polytopic and its exact projection can be determined computationally.

A set $C_n(\T)$ approximating the $n$-step controllable set $\C_n(\T)$ is then given by the solution of the optimisation:
%
\begin{subequations}\label{seq:optimisation:n:step:set:abstract}
\begin{align}
	& \max_{\V^\prime} \vol(C_n(\T))
%\end{equation}
\intertext{subject to}
%\begin{align}
	& \V^\prime\subseteq\V  \\
% \end{equation}
% %
% \begin{equation}
	& \vol(\V^\prime)\geq p\cdot\vol(\V)
\end{align}
\end{subequations}
The property $C_n(\T)\subseteq \C_n(\T)$ then guarantees the existence of a control sequence such that the constraints~(\ref{eq:state_input:constraints}) and (\ref{eq:probabilistic:constraint}) are met and $x_n\in\T$ for all $x_0\in C_n(\T)$.

@@

The underlying probability distribution was assumed to be uniform for ease of presentation, a similar method may be applied to more general distributions as long as they allow the probability measure of a parallelotope to be analytically determined.
%
Future work will remove this restriction by approximating non-uniform probability distributions as discrete distributions defined by collections of spatially distributed point masses.
%
This would necessarily introduce a degree of uncertainty in the probability measure of $\V^\prime$. However the uncertainty would be subject to deterministic bounds (rather than the statistical bounds provided by sample based approaches), which would allow for guarantees of constraint satisfaction.
